A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-17 writeup/paper.tex

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &129,049\\
How many years have you spoken [HIT language]?&159,807\\
How many years have you spoken English?&159,808\\
What country do you live in?&329,033

Current location (collected automatically)& 329,033

\hline\\
Total assignments& 329,033\\
Total unique workers& 6,034

\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
IGNORE TABLE& WILL FIX SOON&\\
&\# languages&\# Turkers\\
\hline
No languages&0&2555

One language&1&2651

Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
\begin{figure}[h]
\centering
\begin{tabular}{cccc}\hline\hline\\
&Avg. & 99\%&\\
&Quality & Conf. Int.&n\\
Misreport&0.252&(0.244, 0.260)&10,479\\
Correct&0.282&(0.280, 0.283)&296,911\\
Overall&0.281&(0.279, 0.282)&307,390

\hline\hline
\end{tabular}
\label{mism-tab}
\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &129,049\\
How many years have you spoken [HIT language]?&159,807\\
How many years have you spoken English?&159,808\\
What country do you live in?&329,033\\
Current location (collected automatically)& 329,033\\
\hline\\
Total assignments& 329,033\\
Total unique workers& 6,034\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
IGNORE TABLE& WILL FIX SOON&\\
&\# languages&\# Turkers\\
\hline
No languages&0&2555\\
One language&1&2651\\
Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
\begin{figure}[h]
\centering
\begin{tabular}{cccc}\hline\hline\\
&Avg. & 99\%&\\
&Quality & Conf. Int.&n\\
Misreport&0.252&(0.244, 0.260)&10,479\\
Correct&0.282&(0.280, 0.283)&296,911\\
Overall&0.281&(0.279, 0.282)&307,390\\
\hline\hline
\end{tabular}
\label{mism-tab}
\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
